---
title: "和歌山県報告書(under working for final report)"
subtitle: "健康寿命"
author: "李鍾賛(jc lee, 滋賀大助教、数理統計学博士)"
date: "最終更新: `r format(Sys.time(), '%Y/%m/%d')`"
output:
  # word_document:
  html_document:
   number_section: true
   toc: true
   code_folding: hide
   # toc_float:
   #   smooth_scroll: false
   #   collapsed: false

# output:
#   ioslides_presentation:
#   widescreen: true
#   number_section: true
#   toc: true
#   transition: faster
  # css: 'scrollable_slides.css'

# runtime: shiny
# https://bookdown.org/yihui/rmarkdown/ioslides-presentation.html

# The following single character keyboard shortcuts enable alternate display modes:
#
# 'f': enable fullscreen mode
#
# 'w': toggle widescreen mode
#
# 'o': enable overview mode
#
# 'h': enable code highlight mode
#
# 'p': show presenter notes
---
```{r}
```


# pre materials- library etc..
```{r}
# devtools::install_github(repo = "luka3117/JcPackage/OsakaUniv2020")

# 使用package
suppressMessages(library(readxl))
suppressMessages(library(dplyr))
suppressMessages(library(data.table))
suppressMessages(library(kableExtra))
suppressMessages(library(curl))
suppressMessages(library(tidyverse))
suppressMessages(library(plotly))
suppressMessages(library(ggrepel))
suppressMessages(library(magrittr))


load("../ScreenEnd.RData")
```

# regression{.tabset .tabset-fade .tabset-pills}

  - only the followings are valid obj
  - d , var, pref_id
  - d_f_merge_X, d_m_merge_X, y_f , y_m
  - LE_d_f_final, HLE_d_f_final, LE_d_m_final, HLE_d_m_final
  - 女性：18変数、男性：11変数


<!-- ```{r child="ref1.Rmd"} -->
<!-- ``` -->

## regression `LE_d_f_final`: 女性、平均寿命
```{r}
# -----------------
# Q1:Do the final regression and interprete : with 4 data
# -----------------
# ----------------- ----------------- ----------------- -----------------
#  _____ _             _   _     __  __
# |  ___(_)_ __   __ _| | | |   |  \/  |
# | |_  | | '_ \ / _` | | | |   | |\/| |
# |  _| | | | | | (_| | | | |___| |  | |
# |_|   |_|_| |_|\__,_|_| |_____|_|  |_|
# ----------------- ----------------- ----------------- -----------------

options(digits = 5)              # Modify global options

lm(LE_2015~. , data = LE_d_f_final) %>%
  broom::tidy() %>%
  left_join(var, by=c("term"="var_name_Eng")) %>%
  select(term, var_name_Jpn, everything(), -id,- address, -std.error, -columm_letter ) %>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'statistic', "p.value"), digits=3)

```

## regression `HLE_d_f_final`: 女性、健康寿命
```{r}
# -----------------
# Q1:Do the final regression and interprete : with 4 data
# -----------------
# ----------------- ----------------- ----------------- -----------------
#  _____ _             _   _     __  __
# |  ___(_)_ __   __ _| | | |   |  \/  |
# | |_  | | '_ \ / _` | | | |   | |\/| |
# |  _| | | | | | (_| | | | |___| |  | |
# |_|   |_|_| |_|\__,_|_| |_____|_|  |_|
# ----------------- ----------------- ----------------- -----------------

options(digits = 5)              # Modify global options

lm(HLE_2016~. , data = HLE_d_f_final) %>%
  broom::tidy() %>%
  left_join(var, by=c("term"="var_name_Eng")) %>%
  select(term, var_name_Jpn, everything(), -id,- address, -std.error, -columm_letter ) %>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'statistic', "p.value"), digits=3)

```





## regression `LE_d_m_final`: 男性、平均寿命
```{r}
# -----------------
# Q1:Do the final regression and interprete : with 4 data
# -----------------
# ----------------- ----------------- ----------------- -----------------
#  _____ _             _   _     __  __
# |  ___(_)_ __   __ _| | | |   |  \/  |
# | |_  | | '_ \ / _` | | | |   | |\/| |
# |  _| | | | | | (_| | | | |___| |  | |
# |_|   |_|_| |_|\__,_|_| |_____|_|  |_|
# ----------------- ----------------- ----------------- -----------------

options(digits = 5)              # Modify global options

lm(LE_2015~. , data = LE_d_m_final) %>%
  broom::tidy() %>%
  left_join(var, by=c("term"="var_name_Eng")) %>%
  select(term, var_name_Jpn, everything(), -id,- address, -std.error, -columm_letter ) %>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'statistic', "p.value"), digits=3)

```



## regression `HLE_d_m_final`: 男性、健康寿命
```{r}
# -----------------
# Q1:Do the final regression and interprete : with 4 data
# -----------------
# ----------------- ----------------- ----------------- -----------------
#  _____ _             _   _     __  __
# |  ___(_)_ __   __ _| | | |   |  \/  |
# | |_  | | '_ \ / _` | | | |   | |\/| |
# |  _| | | | | | (_| | | | |___| |  | |
# |_|   |_|_| |_|\__,_|_| |_____|_|  |_|
# ----------------- ----------------- ----------------- -----------------

options(digits = 5)              # Modify global options

lm(HLE_2016~. , data = HLE_d_m_final) %>%
  broom::tidy() %>%
  left_join(var, by=c("term"="var_name_Eng")) %>%
  select(term, var_name_Jpn, everything(), -id,- address, -std.error, -columm_letter ) %>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'statistic', "p.value"), digits=3)

```


# FA and interprete{.tabset .tabset-fade .tabset-pills}
## 女性説明変数 : X_f

```{r}
LE_d_f_final.reg<-lm(LE_2015~. , data = LE_d_f_final)
d_f_.FA<-LE_d_f_final.reg$model[,-1] %>% zemi::JcFA()
rownames(d_f_.FA$VAR.rotate)<-colnames(LE_d_f_final.reg$model[,-1] )
d_f_.FA$VAR.rotate %>% data.frame() %>% rownames_to_column() %>%
    left_join(var, by=c("rowname"="var_name_Eng")) %>%
  select(rowname,var_name_Jpn,X1,X2) %>% rename(F1=X1, F2=X2) %>%
  DT::datatable() %>% DT::formatRound(columns=c('F1', 'F2'), digits=3)
```


```{r}
d_f_.FA$OBS.rotate %>% as.data.frame() %>% tbl_df() %>%
  rename(F1=V1, F2=V2) %>%
  mutate(pref.J=d_common$pref.J)%>% select(pref.J, everything()) %>%
  DT::datatable() %>% DT::formatRound(columns=c('F1', 'F2'), digits=3)
```

```{r}
#
#
# aa$VAR[,c(1:3)] %>% round(2)
#
#
# plot(aa$OBS.rotate,
#   aa$VAR.rotate)
# DT::datatable()
# aa=zemi::JcFA(zemi::USCrime)
#
# X_f<-LE_d_f_final.reg$model[,-1]
# X_f %>% dim()
#
#  
#
# aa$d
# aa=zemi::JcFA(LE_d_f_final[,-1])
#
# HLE_d_f_final %>% colnames()
# #
# # aa$d
# # aa$OBS
# # aa$VAR
#


```



## 男性説明変数　X_m

```{r}
LE_d_m_final.reg<-lm(LE_2015~. , data = LE_d_m_final)
d_m_.FA<-LE_d_m_final.reg$model[,-1] %>% zemi::JcFA()
rownames(d_m_.FA$VAR.rotate)<-colnames(LE_d_m_final.reg$model[,-1] )
d_m_.FA$VAR.rotate %>% data.frame() %>% rownames_to_column() %>%
    left_join(var, by=c("rowname"="var_name_Eng")) %>%
  select(rowname,var_name_Jpn,X1,X2) %>% rename(F1=X1, F2=X2) %>%
  DT::datatable() %>% DT::formatRound(columns=c('F1', 'F2'), digits=3)
```


```{r}
d_m_.FA$OBS.rotate %>% as.data.frame() %>% tbl_df() %>%
  rename(F1=V1, F2=V2) %>%
  mutate(pref.J=d_common$pref.J)%>% select(pref.J, everything()) %>%   
  DT::datatable() %>% DT::formatRound(columns=c('F1', 'F2'), digits=3)
```




# Regression : 寿命＜ーF1, F2, and interprete{.tabset .tabset-fade .tabset-pills}

## regression : 女性、平均寿命

```{r}
lm(LE_d_f_final$LE_2015~d_f_.FA$OBS.rotate) %>% broom::tidy() %>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'std.error', 'statistic', 'p.value'), digits=3)
lm(LE_d_f_final$LE_2015~d_f_.FA$OBS.rotate) %>% broom::glance()
```

## regression : 女性、健康寿命
```{r}
lm(HLE_d_f_final$HLE_2016~d_f_.FA$OBS.rotate) %>% broom::tidy()%>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'std.error', 'statistic', 'p.value'), digits=3)
lm(HLE_d_f_final$HLE_2016~d_f_.FA$OBS.rotate) %>% broom::glance()
```


## regression : 男性、平均寿命

```{r}
lm(LE_d_m_final$LE_2015~d_m_.FA$OBS.rotate) %>% broom::tidy()%>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'std.error', 'statistic', 'p.value'), digits=3)
lm(LE_d_m_final$LE_2015~d_m_.FA$OBS.rotate) %>% broom::glance()
```

## regression : 男性、健康寿命

```{r}
lm(HLE_d_m_final$HLE_2016~d_m_.FA$OBS.rotate) %>% broom::tidy()%>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'std.error', 'statistic', 'p.value'), digits=3)
lm(HLE_d_m_final$HLE_2016~d_m_.FA$OBS.rotate) %>% broom::glance()
```



# Q2:logistic regression the final regression and interprete {.tabset .tabset-fade .tabset-pills}

## To binary LE and HLE


```{r}
LE_d_f_final$LE_binary <- ifelse(LE_d_f_final$LE_2015>median(LE_d_f_final$LE_2015),1,0)
HLE_d_f_final$HLE_binary <- ifelse(HLE_d_f_final$HLE_2016>median(HLE_d_f_final$HLE_2016),1,0)
LE_d_m_final$LE_binary <- ifelse(LE_d_m_final$LE_2015>median(LE_d_m_final$LE_2015),1,0)
HLE_d_m_final$HLE_binary <- ifelse(HLE_d_m_final$HLE_2016>median(HLE_d_m_final$HLE_2016),1,0)

LE_d_f_final$LE_binary   # 女性
HLE_d_f_final$HLE_binary   # 女性
LE_d_m_final$LE_binary   # 男性
HLE_d_m_final$HLE_binary   # 男性

```

## logit model 女性、LE

```{r}
glm(LE_d_f_final$LE_binary ~ d_f_.FA$OBS.rotate, family =  "binomial")%>% broom::tidy() %>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'std.error', 'statistic', 'p.value'), digits=3)
```


## logit model 女性、HLE


```{r}
glm(HLE_d_f_final$HLE_binary ~ d_f_.FA$OBS.rotate, family =  "binomial")%>% broom::tidy() %>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'std.error', 'statistic', 'p.value'), digits=3)
```


## logit model 男性、LE


```{r}
glm(LE_d_m_final$LE_binary ~ d_m_.FA$OBS.rotate, family =  "binomial")%>% broom::tidy() %>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'std.error', 'statistic', 'p.value'), digits=3)
```

## logit model 男性、HLE

```{r}
glm(HLE_d_m_final$HLE_binary ~ d_m_.FA$OBS.rotate, family =  "binomial")%>% broom::tidy() %>% DT::datatable() %>% DT::formatRound(columns=c('estimate', 'std.error', 'statistic', 'p.value'), digits=3)
```


# try glmm and  interprete

glmmML


# gamma dist ????


# find correlated variable



# data 標準化
<!-- d_common_standarize<- -->
<!-- d_common %>% dplyr::select_if(is.numeric) %>% -->
<!--   select(-key, -pref.id) %>% scale() %>% tbl_df() -->
