---
title: "R code for Chapter4"
author: "JC Lee"
date: "最終更新: `r format(Sys.time(), '%Y/%m/%d')`"
output:
  html_document:
    toc_float: true
    toc: true
    number_section: true
    code_folding: hide
    
fig_width: 9
fig_height: 6
--- 

# needed packages
```{r}
library(OsakaUniv2020)
suppressMessages(library(tidyverse))

# our class pkg
# library(devtools)
# devtools::install_github(repo = "luka3117/JcPackage/OsakaUniv2020")
# remove.packages("OsakaUniv2020")
# help(package = "OsakaUniv2020")
library(OsakaUniv2020)
packageVersion("OsakaUniv2020")
```

# page 121 table 4.2 snoring data 
##  Snoring data Linear prob model with yes-no form 
```{r}
table4.2<-OsakaUniv2020::table4.2
table4.2 %>% round(2) %>% DT::datatable()
plot(p~snoring, data = table4.2)
```



:::: {style="display: flex;"}
:::{}
## response varaible(yes-no form)
```{r}
table4.2.response<-table4.2[, c(1, 2)] %>% as.matrix.data.frame()
table4.2.response %>% knitr::kable()
```
:::
:::{}
## explanatory varaible(yes-no form)
```{r}
table4.2 %>% select(snoring) %>% knitr::kable()
```
:::
::::


```{r}
res.linear.prob.YNform <-
  glm(table4.2.response ~ table4.2$snoring,
  family = binomial(link = "identity"))

res.linear.prob.YNform

res.linear.prob.YNform$fitted.values

table4.2 %>% cbind(res.linear.prob.YNform$fitted.values) %>% select(yes, no, p, hatp=6, snoring) %>% round(2)

  plot(p~snoring, data = table4.2)
  points(res.linear.prob.YNform$fitted.values~table4.2$snoring, col="red")
  abline(res.linear.prob.YNform, col="red")
  abline(lm(table4.2$p ~ table4.2$snoring, weights = table4.2$n), col="blue")

```

```{r}
res.linear.prob.YNform %>% broom::tidy()
res.linear.prob.YNform %>% broom::glance()
res.linear.prob.YNform %>% broom::augment() %>% round(2) %>% knitr::kable()
res.linear.prob.YNform %>% logLik()
```

## check log-likeloihood
```{r}
total<-res.linear.prob.YNform$model %>% select(1) %>% apply(1, sum)
yes<-res.linear.prob.YNform$model$table4.2.response[,1]
pi<-res.linear.prob.YNform %>% broom::augment() %>% select(.fitted) %>% .[[1]]
cbind(total, yes, fitted.pi=pi, binom.prob=dbinom(x = yes, size = total, prob = pi))
```


:::: {style="display: flex;"}
:::{}
```{r}
res.linear.prob.YNform %>% logLik()
```
:::
:::{}
- $Y_i \sim B(n_i, \pi_i)$
- $L=log(\Pi_{1}^{n} P(Y=i|\pi_i))=\sum log(P(Y=i|\pi_i))$
- $-2L=\sum log(P(Y=i|\pi_i))$
```{r}
dbinom(x = yes, size = total, prob = pi) %>% log() %>% sum() %>% "*"(-2)
```
:::
::::


## Linear prob model with long form

:::: {style="display: flex;"}
:::{}
```{r}
table4.2.long <- OsakaUniv2020::table4.2.long
table4.2.long %>% DT::datatable()
```
:::
:::{}
```{r}
#xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx
glm(table4.2.long$DZ~., family =binomial(link = "identity"), data = table4.2.long) %>%broom::tidy()
```
:::
::::



## snoring data  logit model estimation page 123  
```{r}
(m.logit<-glm(cbind(yes, no) ~ snoring, family=binomial(logit)))
round(m.logit$coefficients, 2)
m.logit$fitted.values
```

## page 124 probit model estimation
```{r}
(m.probit<-glm(cbind(yes, no) ~ snoring, family=binomial(probit)))
round(m.probit$coefficients, 2)
m.probit$fitted.values
```


```{r}
plot(p~snoring, data = table4.2)
a<-m.logit$coefficients[1]
b<-m.logit$coefficients[2]

name <- function(x) {
  temp<-a+b*x
  exp(temp)/(1+exp(temp))
}
curve(name, add = T, col="red")
```




# crab data
## crab data summary
- response variable : sattellite

```{r}
crab<-OsakaUniv2020::crab
crab %>% DT::datatable()


theme_set(theme_bw())  # pre-set the bw theme.
g  <- ggplot(data = crab, aes(y = satell, x = width))

g + geom_point()+
  
  geom_smooth(method = "loess", se = F)+
  
  labs(subtitle="width", y="# of sattellite", 
     x="width(cm)",   title="horshoe crab data")


```



## page 126 loglinear GLM for crab data 
```{r}
crab<-OsakaUniv2020::crab
# crab<-read.table("crab.txt", header=T)
m.poisson<-glm(satell~ width, data=crab, family=poisson)
m.poisson %>% broom::tidy() %>% column_to_rownames("term") %>% round(2)
```

```{r}
m.poisson$coefficients
```
##  negative binomial vs identity model(page 131)
```{r}
# library(MASS)
nb<-MASS::glm.nb(satell~ width, data=crab, link=identity, start=coef(m.poisson))

id.poisson<-glm(satell~ width, data=crab, family=poisson(link=identity)
, start=coef(m.poisson))

```

:::: {style="display: flex;"}
:::{}
```{r}
nb %>% broom::tidy() %>% column_to_rownames("term") %>% round(2) %>% DT::datatable()
```
:::
:::{}
```{r}
id.poisson %>% broom::tidy() %>% column_to_rownames("term") %>% round(2) %>% DT::datatable()
```
:::
::::

## crab data grouped

```{r}
OsakaUniv2020::crab_group %>% knitr::kable()

##   Width.interval Width Cases Satellites Mean Variance

crab_group<-OsakaUniv2020::crab_group
theme_set(theme_bw())  # pre-set the bw theme.
g  <- ggplot(data = crab_group, aes(x = Width, y = Mean))
g + geom_point() + xlim(20,32)+
  geom_smooth(method = "loess", se = F)+
  
  stat_function(
  fun = function(x)
  id.poisson$coefficients[1] + x * id.poisson$coefficients[2]
  ) +
  
  stat_function(
  fun = function(x)
  exp(m.poisson$coefficients[1] + x * m.poisson$coefficients[2])
  ,
  col = "red"
  ) +
  
  labs(
  title = "poisson vs identity",
  subtitle = "GLM of crab",
  y = "mean of sattellite",
  x = "width"
  )
#   geom_abline()
#   geom_jitter(width = .5, size=1) +
```


## 

<iframe width="560" height="315" src="https://www.youtube.com/embed/7VGPUBWGv6g" frameborder="0" allowfullscreen>
</iframe>
